\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\pagenumbering{gobble}

\begin{document}
Accra, Ghana \hfill \today

Dear Hiring Team at OpenAI,

I am writing to express my enthusiastic interest in the Engineer position. With 7+ years of experience in AI engineering, specializing in Reinforcement Learning and Deep Learning, and a proven track record of deploying scalable AI systems in production, I am confident I possess the strong Python skills and practical expertise you are seeking.

My background aligns perfectly with your requirements for strong Python skills, familiarity with ML frameworks, and a passion for applying AI in production. I have extensive experience in designing, deploying, and maintaining intelligent systems, ensuring they are scalable and performant.

\begin{itemize}
\item At BoardAndGo, I designed and deployed AI agents for real-time travel assistance, directly applying AI in production environments.\item I optimized backend services using FastAPI and Docker, demonstrating proficiency with modern web frameworks and containerization for deploying scalable systems.\item My project, UmukoziHR Resume Tailor, further showcases my ability to integrate ML frameworks like the Gemini LLM for practical applications, built with FastAPI and Next.js.\end{itemize}

I am particularly drawn to opportunities that involve applying AI to solve real-world challenges and contribute to innovative, scalable solutions. I am eager to contribute my expertise in building and deploying robust AI systems to your team.

Thank you for considering my application. I am eager to discuss how my skills and experience can contribute to your team and look forward to the opportunity to connect.

Sincerely,\\
Jason Quist
\end{document}