\documentclass[11pt]{article}
\usepackage[margin=0.9in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\setlist[itemize]{noitemsep, topsep=0pt,leftmargin=*}
\pagenumbering{gobble}

\begin{document}
{\LARGE Jason Quist}\\
jasonquist.ssh@gmail.com • +233 55 123 4567 • Accra, Ghana
\vspace{4pt}\hrule\vspace{6pt}

\textbf{Summary}\\
AI Engineer with 7+ years of experience building intelligent systems, specializing in Reinforcement Learning, Deep Learning, and multi-agent frameworks. Proven track record of shipping production AI systems and leading small teams, with strong Python skills and expertise in deploying scalable solutions.
\vspace{6pt}\hrule\vspace{6pt}

\textbf{Skills}\\
Python, FastAPI, Next.js, Reinforcement Learning, Deep Learning, Docker, Git
\vspace{6pt}\hrule\vspace{6pt}

\textbf{Experience}\\
\textbfAI Engineer --- BoardAndGo \hfill 2022-01--present\\
\begin{itemize}
\item Designed and deployed AI agents for real-time travel assistance, applying AI in production.\item Optimized backend services with FastAPI and Docker, enhancing system efficiency and scalability.\item Built and maintained multi-agent orchestration pipelines, ensuring robust system operations.\end{itemize}

\textbf{Projects}\\
\textbfResurator \hfill FastAPI, Next.js, LaTeX, Gemini API\\
\begin{itemize}
\item Automated tailored resume and cover letter generation, integrating Gemini LLM for ATS-friendly content.\item Developed a full-stack application using FastAPI and Next.js, demonstrating modern web framework proficiency.\item Built and deployed the system within 24 hours, showcasing rapid development and deployment capabilities.\end{itemize}

\textbf{Education}\\
\textbfCODE --- Bachelors of Software \hfill 2019–2023\\

\end{document}