\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\pagenumbering{gobble}

\begin{document}
Accra, Ghana \hfill \today

Dear Hiring Team at OpenAI,

Dear Hiring Team, I am writing to express my keen interest in the AI Engineer position. With 7+ years of experience in building and deploying intelligent systems, I am confident in my ability to contribute effectively to your team.

My background aligns perfectly with your requirements for strong Python skills, familiarity with ML frameworks, and a passion for applying AI in production. I have a proven track record of designing, deploying, and optimizing scalable AI systems, and I am adept at writing clean, maintainable code.

\begin{itemize}
\item At BoardAndGo, I designed and deployed AI agents for real-time travel assistance and built multi-agent orchestration pipelines, demonstrating my capability in deploying scalable systems.\item I also optimized backend services using FastAPI and Docker, showcasing my proficiency with modern web frameworks and containerization.\item My project, Resurator, further highlights my ability to apply AI in production by automating tailored resume and cover letter generation through the integration of the Gemini LLM, developed and deployed within 24 hours.\end{itemize}

I am particularly drawn to opportunities that involve collaborating with research teams and deploying innovative, scalable solutions, which aligns well with the responsibilities outlined in your job description.

Thank you for considering my application. I am eager to discuss how my skills and experience can benefit your team. I have attached my resume for your review and look forward to hearing from you soon.

Sincerely,\\
Jason Quist
\end{document}