\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\pagenumbering{gobble}

\begin{document}
San Francisco, CA \hfill \today

Dear Hiring Team at Google,

I am writing to express my enthusiastic interest in the Senior Software Engineer position, as advertised. With over 5 years of experience in full-stack development, I am confident my skills align perfectly with your requirements.

My career has focused on developing robust software solutions, with a strong emphasis on Python, microservices, and cloud technologies. I have a proven track record of leading complex projects from conception to deployment, consistently delivering high-quality, scalable systems.

\begin{itemize}
\item Successfully led the development of a microservices architecture that served over 1 million users, demonstrating expertise in scalable system design.\item Engineered and implemented CI/CD pipelines, which significantly reduced deployment times by 60%, enhancing operational efficiency.\item Provided mentorship to junior developers, fostering team growth and ensuring adherence to best practices in software development.\end{itemize}

I am particularly drawn to this opportunity by your company's reputation for innovation and commitment to cutting-edge technology. I am eager to contribute my expertise to a dynamic team that values technical excellence and impactful solutions.

Thank you for considering my application. I am available for an interview at your earliest convenience and look forward to discussing how my skills and experience can benefit your team.

Sincerely,\\
John Doe
\end{document}